### 2007-01-15 Documentation/appendix.tex
*** empty log message ***

Super-Kamiokande Water Cerenkov detector is taken to be $\mathrm{m_{det} = 2.5 \,kt}$ at a baseline of

@@

\subsection*{Variable neutrino factory with Silver Channel -- {\tt NF\_GoldSilver.glb}}

>>>>

Super-Kamiokande Water Cerenkov detector is taken to be $\mathrm{m_{det} = 22.5 \,kt}$ at a baseline of

@@

\subsection*{Variable neutrino factory with Silver Channel -- \\{\tt NF\_GoldSilver.glb}}
